Refactoring `nls()`: a constructive critique

### 2023-02-03 RefactoringNLS/JNAB230203.Rmd
Add another section

>>>>

### More general termination tests

The convergence criterion above, the principal termination control of `nls()`, leaves out 
some possibilities that could
be useful for some problems. The package `nlsr` (@nlsr2019manual) already offers both 
the safeguarded relative offset test (**roffset**) as well as a **small sum of 
squares** test (**smallsstest**) that compares the latest evaluated sum of squared
(weighted) residuals to `e4` times the initial sum of squares, where
`e4 <- (100*.Machine$double.eps)^4` is approximately 2.43e-55.

We note that `nls()` uses a termination test to stop after `maxiter` "iterations". 
Unfortunately, the meaning of "iteration" varies among programs and requires 
careful examination of the
code. We prefer to use the number of times the residuals or the jacobian have
been computed and put upper limits on these. Our codes exit (terminate) when these limits
are reached. Generally we prefer larger limits than the default `maxiter = 50` of `nls()`,
but that may reflect the more difficult problems we have encountered because 
users consult us when standard tools have given unsatisfactory results.
